---
title: "Reproducible Research Assignment 1"
author: "Scott Hansen"
date: "Sunday February 14, 2016"
output: html_document
---
Load necessary libararies

```{r}
library(dplyr)
library(stringr)
library(ggplot2)
library(Hmisc)
library(timeDate)
```

1.  Code for Reading in the data set and/or processing the data

```{r}

setwd("E:\\Data Scientist\\Data Science Track\\Reproducible Reseearch\\Project 1\\Reproducible-Research-Project-1")
IntervalData<- data.frame(read.csv("activity.csv", stringsAsFactors = FALSE, header = TRUE))

```


- Preprocess Data Convert interval to time


```{r}

IntervalData$DateTime<-paste(IntervalData$date, str_pad(IntervalData$interval, 4,side="left", pad="0"))


```

2.  Histogram of the total number of steps taken each day


```{r}

DailyTotalSteps<-tapply(IntervalData$steps, IntervalData$date, sum, na.rm=TRUE)

hist(DailyTotalSteps, breaks=7)

  
```

3.  Mean and Median of steps taken each day  
  
```{r, echo=TRUE} 
MeanSteps<-mean(DailyTotalSteps)
MedianSteps<-median(DailyTotalSteps)

```

-Mean 
```{r}
MeanSteps 
```

-Median 
```{r}
MedianSteps 
```

4.  Time series plot of the average steps taken

```{r}
AvgStepsPerInterfal<- IntervalData[!is.na(IntervalData$steps),]%>%
group_by(interval)%>% 
summarise(Avg=mean(steps))

qplot(interval, Avg, data=AvgStepsPerInterfal, geom="line", xlab="5-minute interval", ylab="Avg # of Steps")

```

5.  5 minute interval that on average contains the maximum number of steps

* The maximum number of steps occurs at interval

```{r}

mostSteps <- which.max(AvgStepsPerInterfal$Avg)

MaxInterval <-AvgStepsPerInterfal[mostSteps,]

MaxInterval$interval

```

6.  Code to determine how to impute missing data
* I selected the mean of all steps to replace missing values

```{r}

IntervalDataClean<-IntervalData
IntervalDataClean$steps<-impute(IntervalDataClean$steps, fun=mean)

```
7.  Histogrram of the total number of steps taken after missing values are imputed  

```{r}

DailyTotalSteps.i<-tapply(IntervalDataClean$steps, IntervalData$date, sum)
hist(DailyTotalSteps.i, breaks=7)


MeanSteps.i<-mean(DailyTotalSteps.i)
MedianSteps.i<-median(DailyTotalSteps.i)

```

8.  Panel plot comparing the average number of steps taken per 5-minute Interval across weekdays and week

```{r}

IntervalDataClean$DayType<- ifelse(isWeekday(IntervalDataClean$date, wday = 1:5), 'WeekDay', 'WeekEnd')

IntervalDataClean.S<-aggregate(steps~interval+DayType, data=IntervalDataClean, mean)


qplot(interval, steps, data=IntervalDataClean.S, geom="line", facets=.~DayType, color=DayType, xlab="5-minute interval", ylab="Avg # of Steps")

